### 2020-08-24 latex/vlp.tex
Small update to begin describing the VLP model

\section{The VLP Constraint}
% TODO: Go through the development of the constraint and prove it gains energy
% TODO: Explain how we came up with the constraint first. Talk about the child
% on a swing, the paper showing the time-optimal control input, and describe why
% we want to remove time from the equation. Discuss the lmin and lmax choices.
% Why do we need to use a VNHC instead of a VHC: we are modelling the
% time-optimal controller in a time-independent way, which requires knowledge of
% which quadrant in (q,p)-space we're in. This means using the angle theta,
% which is inherently a VNHC.

>>>>

\section{The VLP Constraint}
% TODO: Go through the development of the constraint and prove it gains energy
% TODO: Explain how we came up with the constraint first. Talk about the child
% on a swing, the paper showing the time-optimal control input, and describe why
% we want to remove time from the equation. Discuss the lmin and lmax choices.
% Why do we need to use a VNHC instead of a VHC: we are modelling the
% time-optimal controller in a time-independent way, which requires knowledge of
% which quadrant in (q,p)-space we're in. This means using the angle theta,
% which is inherently a VNHC.
We return once again to the example of a person standing on a swing.
Condensing them into a center of mass gives a VLP model of their motion, where
the pendulum shrinks when the person stands and lengthens when they squat
(as in Figure \ref{fig:child-vlp}).
\begin{figure}
   \centering
   \begin{subfigure}[t]{0.5\textwidth}
      % TODO: Insert child standing figure + caption
   \end{subfigure}
   \begin{subfigure}[t]{0.5\textwidth}
      % TODO: Insert child squatting figure + captions
   \end{subfigure}
   \caption{The variable length pendulum representation of a child on a
   swing}\label{fig:child-vlp}
\end{figure}
